\mychapter{1}{\textgamma+jet event classification in LHC collisions}
\label{chap:premierchapitre}

\section{CMS experiment at LHC}

The Compact Muon Solenoid (CMS) is a particle physics detector built on the Large Hadron Collider
(LHC) at CERN in switzerland and France. The goal of CMS experiment is to investigate the physics beyond the Standard
Model.
CMS is designed as a general-purpose detector, capable of studying many aspects of proton collisions at 0.9-13 TeV, the
center-of-mass energy of the LHC particle accelerator.\\
It is made of multiple particle detectors designed to measure the energy and momentum of products of the collisions.
The first layer called the "Tracker" reconstruct the paths of high-energy muons, electrons and hadrons as well as see
tracks coming from the decay of very short-lived particles.\\
Next the "Electromagnetic Calorimeter" is designed to measure with high accuracy the energies of electrons and
photons.\\
The Hadronic Calorimeter measures the energy of hadrons and provides indirect measurement of the presence of
non-interacting, uncharged particles such as neutrinos.\\
Theses layers all fit inside a large solenoid magnet of 3.8 Tesla, this allows the charge/mass ratio of particles to be
determined from the curved track that they follow in the magnetic field.
Finally the "Muon detectors and return yoke" are placed outside of the solenoid.

\section{Hadronic jets in proton-proton collisions}

In particle physics, jets are the experimental signatures of quarks and gluons produced in high-energy processes.\\
These particles having a net colour charge cannot exist freely due to couloour-confinement, thereby they are not
directly observed in nature. Instead, they come together to form colour-neutral hadrons by a process called
hadronisation that leads to a collimated spray of hadrons called a jet.
The detailed understanding of both the jet energy scale and of the transverse momentum resolution is of crucial
importance for many physics analyses.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "isae-report-template"
%%% End: 
